Development of Autograder For Competitive Programming Using Contestant PC As Worker

### 2019-06-29 src/paper.tex
add handling reverse engineering attacks

@@

Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

>>>>

In this work, we don't transfer the raw test-case files to all the workers. Transfering raw test-case files needs a huge bandwidth and can reduce grading performance. Instead of transfering raw test-case file, we transfer the test-case generator program to generate test-case files. The worker receive test-case generator source code from the server and compiles it. The compiled test-case generator program then executed to generates input test-case. The worker uses jury's solution to generates output test-case files. The worker also needs checker program to compare contestant's output with jury's output. The checker program receive contestant's output and jury's output as its input and gives the verdict of the submission.

In order to hide the test-case information, we encrypt the test-case generator program and the generated test-case files. Even though the test-case is encrypted, the contestants might decrypt it if they know the encryption key. The contestant can attacks the autograder program using reverse engineering technique to obtain the encryption key. In this work, we didn't handle this problem. Further research are needed to solve this problem.

@@

Because the autograder programs are deployed in the contestant computers, the contestants can do everything to the program. The contestant can attacks the autograder program in their computer. There are many kind of attacks that the contestant can do such as changing the compiler program, sending the false verdict to the server and refuse to grade other contestant submission. In this work, we didn't handle this kind of attacks, but there is a way to handle this kind of attacks.

We can prevent a contestant to refuse do the grading process by monitoring the grading process. When we find out that there is a worker that not asks for job for a long time or not sends the grading result for a long time, we can tell that there is a contestant that attacks the autograder program in their computer. Then, we can warn or disquafy the contestant for attacking the autograder program.

By grading every submission multiple times, we can prevent a worker from being atacked that cause it gives wrong verdict after grading. When we grade a submission multiple times and there is a contestant that attacks the autograder in their computer, we can tell by investigating the grading result. If the grading result of a worker is different from the rest of workers, we can tell that the contestant attacks the autograder program in that worker. Then, we can warn or disquafy that contestant for attacking the autograder program.

There are many more type of attacks that we didn't handle in this work such as stealing jury's solution, other contestant's solution and test-case generator. Even though we didn't handle some type of attacks, this system can still works in several competition such as ACM-ICPC. In ACM-ICPC, every team is given a computer by the juries to solve the problems. The juries can install autograder program inside contestant's computer using root user and not giving the root access to the contestant. By using this mechanism, the contestant can't attacks the autograder program inside their computer.

\section{Implementation}
